The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-26 paper/ms.tex
peak maxima

\subsection{Line Maxima}
\label{sec:peaks}

@@

In order to quantify the transition to a single peak we measure the
position for the peak maxima as a function of the rotational
velocity. Our results are presented in Figure
\ref{fig:maximumsvsvelocity} where it is clear that for central
sources there are two peaks with fixed positions as the rotational
velocity changes, with the only exception of the model with $\tau_{\rm
  H}=10^6$ and $V_{\rm max}=300$\kms. However, in the case of
homogeneously emitted sources the maxima position remain fixed until
some velocity threshold is reachd and the line becomes single peaked
with $x_{\rm m}=0$. By inspection we find that in all cases the
transition has occurred when the rotational velocity is larger than
half the FWHM.

>>>>

\subsection{Line Maxima}
\label{sec:maxima}

@@

We quantify the transition to a single peak by measuring the peak
maxima position as a function of the viewing angle and the rotational 
velocity. The results are presented in Figure
\ref{fig:maximumsvsvelocity}. There are three interesting features
that deserved attention. First For $|\mu|\sim 1.0$ and central sources
the two peaks have the same position regardless of the rotational
velocity. Second, in the same homogeneous models we see that for increasing
rotational velocities the line becomes single peaked, $x_{m}\sim
0$\kms as $|\mu|\sim 0.0$.
